A Deep Learning Approach for Gait Event Detection from a Single Shank-Worn IMU: Validation in Healthy and Neurological Cohorts

### 2022-04-22 paper/MDPI_template/article.tex
Changed Vecteezy image attribution

\begin{figure}[H]
	\begin{adjustwidth}{-\extralength}{0cm}
		\centering
		\includegraphics[width=13.5cm]{fig/methods_overall_workflow.pdf}
	\end{adjustwidth}
	\caption{Schematic depiction$^{1}$ of the current study. Study participants wore IMUs on the ankle and shanks, and reflective markers were adhered on the heel and toe of usual footwear (illustrated on the left). Marker data were used to obtain reference values for the timings of initial and final contacts (top), where accelerometer and gyroscope data from each tracked point were inputted to a neural network that predicted timings of the same initial and final contacts (bottom). \newline \noindent{\footnotesize{\textsuperscript{1} Picture from: \url{https://www.vecteezy.com/free-vector/man-walking }.}} \label{fig:methods_marker_vs_imu}}
\end{figure}

@@

\acknowledgments{The authors sincerely thank all people that were involved in the data collection, from study participants to students who aided and assisted during measurements and subsequent marker labeling. The authors thank Julius Welzel for his input regarding the organization of the data in a BIDS-like format. The authors thank Johannes Hoffmann for his tips regarding the \LaTeX typesetting.}

>>>>

\begin{figure}[H]
	\begin{adjustwidth}{-\extralength}{0cm}
		\centering
		\includegraphics[width=13.5cm]{fig/methods_overall_workflow.pdf}
	\end{adjustwidth}
	\caption{Schematic depiction$^{1}$ of the current study. Study participants wore IMUs on the ankle and shanks, and reflective markers were adhered on the heel and toe of usual footwear (illustrated on the left). Marker data were used to obtain reference values for the timings of initial and final contacts (top), where accelerometer and gyroscope data from each tracked point were inputted to a neural network that predicted timings of the same initial and final contacts (bottom). \newline \noindent{\footnotesize{\textsuperscript{1} Picture from: \href{https://www.vecteezy.com/free-vector/man-walking}{Man Walking Vectors by Vecteezy}.}} \label{fig:methods_marker_vs_imu}}
\end{figure}

@@

\acknowledgments{The authors sincerely thank all people that were involved in the data collection, from study participants to students who aided and assisted during measurements and subsequent marker labeling. The authors thank Julius Welzel for his input regarding the organization of the data in a BIDS-like format. The authors thank Johannes Hoffmann for his tips regarding the \LaTeX typesetting. The "walking man" picture from Figure~\ref{fig:methods_marker_vs_imu} is from \href{https://www.vecteezy.com/free-vector/man-walking}{Man Walking Vectors by Vecteezy}.}
